Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles

### 2021-05-08 source/tex/ladybug_adhesion.tex

Many insects can climb smooth surfaces using hairy adhesive pads on their legs. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extent such an air bubble is necessary for underwater adhesion. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the tarsal adhesive fluid secretion alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. 
\end{abstract}

@@

The question on how insects and other small animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}. We know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion. Insect tarsal hairs secrete an adhesion-mediating fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hairs when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of adhesive fluid by each step \cite{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water.

The goal of this paper is to provide a generalised picture of underwater adhesion in insects which use hairy pads and secrete an oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \cite{RN145}. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we
discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We characterised adhesion by the pull-off force
during detachment, tested on smooth normal and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact modes were compared for both substrates.

@@

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate. Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 Nm\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element (\emph{Physik Instrumente, Germany}), used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textmu ms\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

@@

Five force measurements were subsequently performed on a fresh spot of the substrate and averaged for data analysis. 
Experiments were repeated five times with unique male beetles for each mode of contact (``\emph{in air}'', (``\emph{underwater:
bubble}'' and (``\emph{underwater: no bubble}'') and substrate (hydrophilic, hydrophobic). Thus, in total, 30 beetles were tested.
%CHECK TYPE OF CONTACT CHANGE TO MODE OF CONTACT%

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion test setup (for explanation see text). The recorded force data and
contact area of a distal pad are shown in the plot, in which, the shaded
regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material.}
\end{figure}

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow. For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA. The surface was then plasma cleaned in a oxygen
plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours. Henceforth, we refer to the hydrophilic normal glass substrate 
as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.

The surface chemistry was characterised by dynamic contact angle
measurements, performed with a contact angle goniometer (\emph{OCA 35, DataPhysics Instruments GmbH, Germany})
The substrate's wetting towards a polar (Milli-Q water) and a non-polar (n-hexadecane) liquid was tested. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textmu l and with 0.5 \textmu ls\protect\textsuperscript{-1} flow rate (Table \ref{tab:Contact-Angles}).

@@

%\subsubsection{Field desorption mass spectroscopy}
%
%A previous study on arachnids \cite{RN223} reported that its secreted
%fluid does not dissolve in water. To test whether the beetles retain
%their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
%(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
%were done on the extracted secretions before and after rinsing its
%legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
%axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
%to the measurement chamber of the FDMS. As a reference, pure THF was
%used. The second middle leg of the same ladybird was subsequently
%immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
%20 min and then transferred to the measurement chamber of the spectrometer.
%Molecular composition was extracted from the peak positions of the
%FDMS spectra.

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on glass (blue) and PFOTS (red) substrates in air and underwater
conditions. The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions (see text) of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mNm\protect\textsuperscript{-1} and 48 mNm\protect\textsuperscript{-1} respectively and water surface tension is 72 mNm\protect\textsuperscript{-1}.}
\end{figure}

Apart from the three depicted contact modes, we observed an additional
fourth type which occurred in roughly 25\% of our underwater experiments.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate, unlike the other
three contact modes (see supplementary info). This ``bad contact'' scenario shows no adhesion %INCLUDE SUPPLEMENTARY%
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

%\subsubsection{Field desorption mass spectroscopy}
%
%FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
%leg when underwater (Table \ref{tab:Molecular-distribution-of}).
%Molecular weights of the secreted fluid mixtures extracted from the
%beetle's leg, without and after immersion in water, show that, except
%for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
%fingerprint remained unchanged. This indicates that the adhesion fluid
%was not washed away underwater. Probable compounds in the fluid, corresponding
%to the resultant molecular weights, include mostly aliphatic hydrocarbons
%with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
%to assert that, even for the case of \emph{Coccinella
%septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments. 
%
%\begin{table}[H]
%\centering{}%
%\begin{tabular}{|c|c|c|}
%\hline 
%Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
%\hline 
%\hline 
%324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
%\hline 
% & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
%\hline 
%350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
%\hline 
%352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
%\hline 
%378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
%\hline 
%404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
%\hline 
%406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
%\hline 
%432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
%\hline 
%\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
%with and without rinsing the beetle's leg in water. \label{tab:Molecular-distribution-of}}
%\end{table}

@@

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate (hydrophilic or hydrophobic) in three ways: a) \emph{In air}, where the tarsal adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the tarsal adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the tarsal adhesive fluid bridges are
inside the bubble while others are outside in water (see text for details). The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}

We modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has an
adhesive fluid of volume, $V_{f}$, making contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
types of contacts for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

>>>>

Many insects can climb smooth surfaces using hairy adhesive pads on their legs mediated by tarsal fluid secretions. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extent such an air bubble is necessary for underwater adhesion. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the tarsal fluid alone can determine the ladybugs'  adhesion to smooth surfaces in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. The study highlights how such a mediating fluid can serve as a potential strategy to achieve underwater adhesion via capillary forces, which could inspire artificial adhesives for underwater applications.
\end{abstract}

@@

The question on how insects and other small animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}. We know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion. Insect tarsal hairs secrete an adhesion-mediating fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN201,RN155,RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \cite{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water.

The goal of this paper is to clarify the current understanding of underwater adhesion seen in terrestrial insects which use hairy pads and secrete an oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \cite{RN145} and they can also walk underwater. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals. We hope our study to provide new strategies to design bio-inspired materials that show good adhesive properties in both air and underwater conditions, similar to what has been previously reported for terrestrial beetles \cite{RN87}.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We focus our study only on a single tarsal adhesive pad of the leg by carefully fixing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion. 
We characterised adhesion by the pull-off force
during detachment, tested on smooth normal and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact modes were compared for both substrates.

@@

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N m\protect\textsuperscript{-1}) constituted
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A
3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element (\emph{Physik Instrumente, Germany}), used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
A coaxial illuminated tube microscope
(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used simultaneously to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

@@

Five force measurements were subsequently performed, each on a fresh spot of the substrate, and averaged for data analysis. 
Experiments were repeated with five distinct male beetles for each combination of contact mode (``\emph{in air}'', (``\emph{underwater:
bubble}'' and (``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic). Thus, in total, 30 distinct beetles were tested. After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion test setup (see text for details). Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange). The recorded force data and
contact area of a distal pad are shown in the bottom-right plot, in which, the shaded
regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material (S2-S4).}
\end{figure}

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (bottom-right plot in Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

Standard 20 mm wide glass cover-slips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow before use. For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapour deposition (CVD). First, the glass
was cleaned using IPA. The surface was then plasma cleaned in an oxygen
plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours. Henceforth, we refer to the hydrophilic normal glass substrate 
as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.

The surface chemistry was characterised by dynamic contact angle
measurements, performed with a contact angle goniometer (\emph{OCA 35, DataPhysics Instruments GmbH, Germany})
The substrate's wetting towards a polar (Milli-Q water) and a non-polar (n-hexadecane) liquid was tested. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textmu l and with 0.5 \textmu l s\protect\textsuperscript{-1} flow rate (Table \ref{tab:Contact-Angles}).

@@

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on normal hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
conditions (n=30). The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions (see text) of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
\end{figure}

Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary video S5), unlike the other
three contact modes (supplementary video S2-S4). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}
\caption{\label{fig:Model}The capillary bridge model of a hairy adhesive pad. The hairs make contact
with the substrate (hydrophilic or hydrophobic) in three modes: a) \emph{In air}, where the tarsal adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the fluid bridges are
inside the bubble while others are outside in water (see text for details). The corresponding
ventral view contact images of the beetle's pad seen during adhesion experiments are shown on the right.}
\end{figure}

We modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
adhesive fluid of volume, $V_{f}$, mediating contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we considered three
modes of contact for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.
